UniScatter: Unifying\\Backscatter Communications, Reconfigurable Intelligent Surface, and Symbiotic Radio

### 2022-08-01 main.tex
:pencil: Update abstract

% glossaries-extra
\setabbreviationstyle[acronym]{long-short}
\newacronym{af}{AF}{Amplify-and-Forward}
\newacronym{ambc}{AmBC}{Ambient Backscatter Communications}
\newacronym{ap}{AP}{Access Point}
\newacronym{awgn}{AWGN}{Additive White Gaussian Noise}
\newacronym{bcd}{BCD}{Block Coordinate Descent}
\newacronym{bibo}{BIBO}{Binary-Input Binary-Output}
\newacronym{bpcu}{\si{bpcu}}{bits per channel use}
\newacronym{bpsphz}{\si{bps/Hz}}{bits per second per Hertz}
\newacronym{cp}{CP}{Canonical Polyadic}
\newacronym{cr}{CR}{Cognitive Radio}
\newacronym{cscg}{CSCG}{Circularly Symmetric Complex Gaussian}
\newacronym{csi}{CSI}{Channel State Information}
\newacronym{df}{DF}{Decode-and-Forward}
\newacronym{dmc}{DMC}{Discrete Memoryless Channel}
\newacronym{dmtc}{DMTC}{Discrete Memoryless Thresholding Channel}
\newacronym{dmtmac}{DMTMAC}{Discrete Memoryless Thresholding Multiple Access Channel}
\newacronym{dtmac}{DTMAC}{Discrete Thresholding Multiple Access Channel}
\newacronym{dp}{DP}{Dynamic Programming}
\newacronym{iid}{i.i.d.}{independent and identically distributed}
\newacronym{kkt}{KKT}{Karush–Kuhn–Tucker}
\newacronym{mac}{MAC}{Multiple Access Channel}
\newacronym{mc}{MC}{Multiplication Coding}
\newacronym{miso}{MISO}{Multiple-Input Single-Output}
\newacronym{mimo}{MIMO}{Multiple-Input Multiple-Output}
\newacronym{ml}{ML}{Maximum-Likelihood}
\newacronym{noma}{NOMA}{Non-Orthogonal Multiple Access}
\newacronym{ofdm}{OFDM}{Orthogonal Frequency-Division Multiplexing}
\newacronym{pdf}{PDF}{Probability Density Function}
\newacronym{pgd}{PGD}{Projected Gradient Descent}
\newacronym{psk}{PSK}{Phase Shift Keying}
\newacronym{qam}{QAM}{Quadrature Amplitude Modulation}
\newacronym{rf}{RF}{Radio-Frequency}
\newacronym{ris}{RIS}{Reconfigurable Intelligent Surface}
\newacronym{sc}{SC}{Superposition Coding}
\newacronym{sic}{SIC}{Successive Interference Cancellation}
\newacronym{simo}{SIMO}{Single-Input Multiple-Output}
\newacronym{sinr}{SINR}{Signal-to-Interference-plus-Noise Ratio}
\newacronym{smawk}{SMAWK}{Shor-Moran-Aggarwal-Wilber-Klawe}
\newacronym{sr}{SR}{Symbiotic Radio}
\newacronym{tdma}{TDMA}{Time-Division Multiple Access}
\newacronym{ue}{UE}{user}
\newacronym{wit}{WIT}{Wireless Information Transfer}
\newacronym{wpcn}{WPCN}{Wireless Powered Communication Network}
\newacronym{wpt}{WPT}{Wireless Power Transfer}

\begin{document}
% \title{UniScatter: Unifying Backscatter Communication, Reconfigurable Intelligent Surface, and Symbiotic Radio}
\title{UniScatter: Unifying Symbiotic Radio and Reconfigurable Intelligent Surface}
\author{
	\IEEEauthorblockN{
		Yang~Zhao,~\IEEEmembership{Member,~IEEE,}
		and~Bruno~Clerckx,~\IEEEmembership{Fellow,~IEEE}
	}
	\thanks{
		The authors are with the Department of Electrical and Electronic Engineering, Imperial College London, London SW7 2AZ, U.K. (e-mail: \{yang.zhao18, b.clerckx\}@imperial.ac.uk).
	}
}
\maketitle

\begin{abstract}
	% Backscatter allows wireless nodes to harvest energy from, modulate information over, and reconfigure propagation of surrounding radio waves.
	% Backscatter nodes can harvest energy from, modulate information over, and reconfigure propagation of ambient signals.
	% Backscatter nodes can harvest energy from, modulate information over, and reconfigure propagation of surrounding radio waves.
	% Scattering/reflection elements to
	% An RIS is a thin surface composed of N elements, each being a reconfigurable scatterer: a small antenna that receives and re-radiates without amplification, but with a configurable time delay [3]. For narrowband signals, this delay corresponds to a phase shift.

	Scatterers can harvest energy from, modulate information over, and reconfigure propagation of ambient radio waves.
	In backscatter communication,
	% ! Φ(c[n]) vs P

	% TODO
	back comms, symbiotic radio and RIS have appeared as three different and somewhat unrelated wireless technologies, explaining the key feature of each of them. Then I would say we introduce metascatter as a new paradigm that unifies and generalizes those three ...., explain the key feature of metascatter.

	We uniquely introduce \emph{Metascatter} that adapts the input distribution of a finite-state passive backscatter node based on \gls{csi}, to \emph{simultaneously} encode self message and assist legacy transmission while powered by surrounding waves.
	% Compared to conventional \gls{ris}-empowered \gls{sr} that encodes and precodes independently (e.g., overlay or parallel), Metascatter refines backscatter principles to bridge parasitic source of \gls{sr} and reflecting element of \gls{ris} as extreme cases.
	Compared to existing \gls{ris}-empowered \gls{sr} that encodes and precodes independently using advanced architecture (e.g., overlay or parallel), Metascatter softly bridges and generalizes parasitic source of \gls{sr} and reflecting element of \gls{ris} via smart input design.
	% Compared to \gls{ris}-empowered \gls{sr} that encodes and precodes independently (e.g., overlay or parallel), Metascatter refines backscatter principles to bridge parasitic source of \gls{sr} and reflecting element of \gls{ris} as extreme cases.
	% Such an integrated distribution design not only yields universal modularity with reduced optimization cost, but also enables a flexible tradeoff between primary and backscatter links using shared spectrum, energy, and infrastructures.
	This not only reduces hardware complexity and optimization cost, but also enables a flexible tradeoff between primary (legacy) and backscatter links using shared spectrum, energy, and infrastructures.
	Moreover, we consider a specific scenario where a multi-antenna \gls{ap} serves a single-antenna user surrounded by multiple Metascatters.
	For simplicity, it is assumed the user first jointly decodes all backscatter messages from accumulated energy, then models reflection patterns and backscatter paths within equivalent channel for primary decoding.
	% Once modulation uncertainty of Metascatters are eliminated, models contributions from additional paths within equivalent channel
	% decodes all Metascatters jointly by energy detection, then models their contribution within equivalent channel and decodes the primary link.
	% For simplicity, the user is assumed first decodes all Metascatters jointly by energy detection, then models their contribution within equivalent channel and decodes the primary link.
	We characterize the achievable primary-(total-)backscatter rate region by optimizing the input distribution at Metascatters, the active beamforming at the AP, and the decision regions at the user.
	% A suboptimal \gls{bcd} algorithm was proposed, where the input distribution satisfying the \gls{kkt} conditions is evaluated in closed form, the transmit beamforming is optimized by \gls{pgd}, and the decision thresholds are optimized by \gls{dp}.
	% A suboptimal \gls{bcd} algorithm is proposed, where the \gls{kkt} input distribution is numerically evaluated in closed form, the active beamforming is iteratively updated by \gls{pgd}, and the decision regions are restricted to convex and opty
	% We then propose a suboptimal \gls{bcd} algorithm that numerically evaluates the \gls{kkt} input distribution in closed form, iteratively updates the active beamforming by \gls{pgd}, and employs existing thresholding schemes to refine suboptimal convex decision regions.
	A suboptimal \gls{bcd} algorithm is proposed, which numerically evaluates the \gls{kkt} input distribution in closed form, iteratively updates the active beamforming by \gls{pgd}, and employs existing thresholding schemes for suboptimal convex decision regions.
	% A suboptimal \gls{bcd} algorithm was proposed with the \gls{kkt} input distribution evaluated in closed form, the active beamforming updated by \gls{pgd}, and the decision regions restricted to convex then refined by \gls{dp}.
	% the decision regions are restricted as convex then optimized by \gls{dp}.
	% A suboptimal \gls{bcd} algorithm was proposed, where the \gls{kkt} input distribution is evaluated in closed form, the active beamforming is optimized by \gls{pgd} with backtracking line search, and the decision thresholds are optimized by \gls{dp}.
	Simulation results demonstrate Metascatters can exploit additional propagation paths to transmit and assist via adaptive input design.
\end{abstract}

@@

	\emph{First,} Metascatter adapts the input probability distribution of a finite-state passive backscatter device based on primary and (cascaded) backscatter \gls{csi} to unify and generalize parasitic source of \gls{sr} and reflecting elements of \gls{ris}.
	The reflection pattern over time is no longer fully random or deterministic, but can be flexibly distributed to balance backscatter encoding and passive beamforming.
	For single-user scenario, when primary link is absolutely prioritized, the distribution falls on one state and Metascatter boils down to conventional \gls{ris}.
	When only considering backscatter performance, the distribution involves the highest entropy and Metascatter is essentially an \gls{ambc} node.

>>>>

% glossaries-extra
\setabbreviationstyle[acronym]{long-short}
\newacronym{af}{AF}{Amplify-and-Forward}
\newacronym{ambc}{AmBC}{Ambient Backscatter Communications}
\newacronym{ap}{AP}{Access Point}
\newacronym{awgn}{AWGN}{Additive White Gaussian Noise}
\newacronym{bcd}{BCD}{Block Coordinate Descent}
\newacronym{bc}{BackCom}{Backscatter Communications}
\newacronym{bibo}{BIBO}{Binary-Input Binary-Output}
\newacronym{bpcu}{\si{bpcu}}{bits per channel use}
\newacronym{bpsphz}{\si{bps/Hz}}{bits per second per Hertz}
\newacronym{cp}{CP}{Canonical Polyadic}
\newacronym{cr}{CR}{Cognitive Radio}
\newacronym{cscg}{CSCG}{Circularly Symmetric Complex Gaussian}
\newacronym{csi}{CSI}{Channel State Information}
\newacronym{df}{DF}{Decode-and-Forward}
\newacronym{dmc}{DMC}{Discrete Memoryless Channel}
\newacronym{dmtc}{DMTC}{Discrete Memoryless Thresholding Channel}
\newacronym{dmtmac}{DMTMAC}{Discrete Memoryless Thresholding Multiple Access Channel}
\newacronym{dtmac}{DTMAC}{Discrete Thresholding Multiple Access Channel}
\newacronym{dp}{DP}{Dynamic Programming}
\newacronym{iid}{i.i.d.}{independent and identically distributed}
\newacronym{kkt}{KKT}{Karush-Kuhn-Tucker}
\newacronym{mac}{MAC}{Multiple Access Channel}
\newacronym{mc}{MC}{Multiplication Coding}
\newacronym{miso}{MISO}{Multiple-Input Single-Output}
\newacronym{mimo}{MIMO}{Multiple-Input Multiple-Output}
\newacronym{ml}{ML}{Maximum-Likelihood}
\newacronym{noma}{NOMA}{Non-Orthogonal Multiple Access}
\newacronym{ofdm}{OFDM}{Orthogonal Frequency-Division Multiplexing}
\newacronym{pdf}{PDF}{Probability Density Function}
\newacronym{pgd}{PGD}{Projected Gradient Descent}
\newacronym{psk}{PSK}{Phase Shift Keying}
\newacronym{qam}{QAM}{Quadrature Amplitude Modulation}
\newacronym{qos}{QoS}{Quality of Service}
\newacronym{rf}{RF}{Radio-Frequency}
\newacronym{ris}{RIS}{Reconfigurable Intelligent Surface}
\newacronym{sc}{SC}{Superposition Coding}
\newacronym{sic}{SIC}{Successive Interference Cancellation}
\newacronym{simo}{SIMO}{Single-Input Multiple-Output}
\newacronym{sinr}{SINR}{Signal-to-Interference-plus-Noise Ratio}
\newacronym{smawk}{SMAWK}{Shor-Moran-Aggarwal-Wilber-Klawe}
\newacronym{sr}{SR}{Symbiotic Radio}
\newacronym{tdma}{TDMA}{Time-Division Multiple Access}
\newacronym{ue}{UE}{user}
\newacronym{wit}{WIT}{Wireless Information Transfer}
\newacronym{wpcn}{WPCN}{Wireless Powered Communication Network}
\newacronym{wpt}{WPT}{Wireless Power Transfer}

\begin{document}
% \title{UniScatter: Unifying Backscatter Communication, Reconfigurable Intelligent Surface, and Symbiotic Radio}
% \title{UniScatter:\\Unifying Backscatter Communication, Reconfigurable Intelligent Surface, and Symbiotic Radio}
\title{UniScatter: Unifying\\Backscatter Communications, Reconfigurable Intelligent Surface, and Symbiotic Radio}
% \title{UniScatter: Unifying Symbiotic Radio, Reconfigurable Intelligent Surface, and Wireless Sensor Network}
% \title{UniScatter: Unifying Symbiotic Radio and Reconfigurable Intelligent Surface}
\author{
	\IEEEauthorblockN{
		Yang~Zhao,~\IEEEmembership{Member,~IEEE,}
		and~Bruno~Clerckx,~\IEEEmembership{Fellow,~IEEE}
	}
	\thanks{
		The authors are with the Department of Electrical and Electronic Engineering, Imperial College London, London SW7 2AZ, U.K. (e-mail: \{yang.zhao18, b.clerckx\}@imperial.ac.uk).
	}
}
\maketitle

\begin{abstract}
	% First, we highlight why NOMA is inefficient in multi-antenna settings based on basic multiplexing gain analysis. We stress that the issue lies in how the NOMA literature, originally developed for single-antenna setups, has been hastily applied to multi-antenna setups, resulting in a misuse of spatial dimensions and therefore loss in multiplexing gains and rate. Second, we show that NOMA incurs a severe multiplexing gain loss despite an increased receiver complexity due to an inefficient use of SIC receivers. Third, we emphasize that much of the merits of NOMA are due to the constant comparison to OMA instead of comparing it to MU–LP and RS baselines. We then expose the pivotal design constraint that multi-antenna NOMA requires one user to fully decode the messages of the other users. This design constraint is responsible for the multiplexing gain erosion, rate and spectral efficiency loss, ineffectiveness to serve a large number of users, and inefficient use of SIC receivers in multi-antenna settings. Our analysis and simulation results confirm that NOMA should not be applied blindly to multi-antenna settings, highlight the scenarios where MU–LP outperforms NOMA and vice versa, and demonstrate the inefficiency, performance loss, and complexity disadvantages of NOMA compared to RSMA. The first takeaway message is that, while NOMA is suited for single-antenna settings (as originally intended), it is not efficient in most multi-antenna deployments. The second takeaway message is that another non-orthogonal transmission framework, based on RSMA, exists which fully exploits the multiplexing gain and the benefits of SIC to boost the rate and the number of users to serve in multi-antenna settings and outperforms both NOMA and MU–LP. Indeed, RSMA achieves higher multiplexing gains and rates, serves a larger number of users, is more robust to user deployments, network loads and inaccurate channel state information and has a lower receiver complexity than NOMA. Consequently, RSMA is a promising technology for NGMA and future networks such as 6G and beyond.

	Scatterers can harvest energy from, modulate information over, and influence propagation of surrounding radio waves.
	\gls{bc} varies object impedance to manipulate the magnitude, phase, and/or frequency of scattered signal to encode information and deliver within coverage.
	\gls{ris} adapts scattering antennas or programmable metamaterial to control propagation environment and boost/suppress signal strength in specific directions.
	\gls{sr} incorporates scatter nodes into active networks, which recycle ambient signal to transmit self information and enhance legacy multipath to the cooperative receiver.
	% In this paper, we depart from those concepts and introduce UniScatter as a new paradigm to support the high throughput, ultralow power, and ubiquitous connectivity of future wireless networks using shared spectrum, energy, and infrastructures.
	In this paper, we depart from those concepts and introduce UniScatter as a new paradigm to support the high throughput, ultralow power, and ubiquitous connectivity of future wireless networks.
	Instead of treating probability distribution of reflection states as equiprobable (as scattering source of \gls{bc}/\gls{sr}) or degenerate (as reflecting element of \gls{ris}), UniScatter node adapts input distribution based on \gls{csi} and link priority to balance information encoding and channel reconfiguration in a mutualistic and flexible manner.
	% Accommodated to signal characteristics, UniScatter receiver semi-coherently decodes all nodes from accumulated energy, re-encodes to determine the equivalent channel, then decodes the primary link to support backscatter modulation and preserve passive beamforming.
	% Accommodated to signal characteristics, UniScatter receiver semi-coherently decodes all nodes from accumulated energy, combines reflection pattern with \gls{csi} for the equivalent channel, then decodes the primary link to support backscatter modulation and preserve passive beamforming.
	To accommodate signal characteristics, UniScatter receiver semi-coherently decodes all nodes from accumulated energy, acquires equivalent primary channel over reflection pattern, then coherently decodes the primary link under enhanced multipath.
	It reduces the complexity of cooperative decoding while preserves the benefit of backscatter modulation and passive beamforming.
	Using shared spectrum, energy, and infrastructures, UniScatter is a more general and powerful transmit-assist protocol that generalizes \gls{bc}, \gls{ris} and \gls{sr} with universal hardware design and augmented \gls{qos} control.
	% Using shared spectrum, energy, and infrastructures, each UniScatter node adapts probability distribution of reflection states based on \gls{csi} to balance information encoding and passive beamforming in a mutualistic and flexible manner.
	% The scatter source of \gls{bc}/\gls{sr} and reflecting element of \gls{ris} can be viewed as extreme cases of UniScatter node, where the input distribution boils down to equiprobable and degenerate, respectively.
	% To accommodate signal characteristics, we propose a practical receiver that semi-coherently decodes all nodes from accumulated energy, re-encodes to determine the equivalent channel, then decodes the primary link.
	% It reduces the complexity of cooperative decoding while preserves the benefit of backscatter modulation and passive beamforming.
	Moreover, we consider an application scenario where a multi-antenna \gls{ap} serves a single-antenna user surrounded by multiple UniScatter nodes, and characterize the achievable primary-(total-)backscatter rate region by designing input distribution at the nodes, active beamforming at the \gls{ap}, and backscatter decision design at the user.
	Simulation results demonstrate UniScatter can flexibly control the transmit-assist tradeoff via smart input distribution design.

	% reduces the complexity of cooperative decoding while preserves the benefit of passive beamforming.
	% reduces the complexity of cooperative decoding while preserves the benefit of backscatter modulation and passive beamforming.

	% In this paper, we argue that to efficiently cope with the high throughput, heterogeneity of quality of service (QoS), and massive connectivity requirements of future multi-antenna wireless networks, multiple access design needs to depart from those two extreme interference management strategies, namely fully treat interference as noise (as in SDMA) and fully decode interference (as in NOMA). Considering a multiple-input single-output broadcast channel, we develop a novel multiple access framework, called rate-splitting multiple access (RSMA). RSMA is a more general and more powerful multiple access for downlink multi-antenna systems that contains SDMA and NOMA as special cases. RSMA relies on linearly precoded rate-splitting with SIC to decode part of the interference and treat the remaining part of the interference as noise. This capability of RSMA to partially decode interference and partially treat interference as noise enables to softly bridge the two extremes of fully decoding interference and treating interference as noise and provides room for rate and QoS enhancements and complexity reduction. The three multiple access schemes are compared, and extensive numerical results show that RSMA provides a smooth transition between SDMA and NOMA and outperforms them both in a wide range of network loads (underloaded and overloaded regimes) and user deployments (with a diversity of channel directions, channel strengths, and qualities of channel state information at the transmitter). Moreover, RSMA provides rate and QoS enhancements over NOMA at a lower computational complexity for the transmit scheduler and the receivers (number of SIC layers).
\end{abstract}

@@

	% ! Φ(c[n]) vs P
	\emph{First,} Metascatter adapts the input probability distribution of a finite-state passive backscatter device based on primary and (cascaded) backscatter \gls{csi} to unify and generalize parasitic source of \gls{sr} and reflecting elements of \gls{ris}.
	The reflection pattern over time is no longer fully random or deterministic, but can be flexibly distributed to balance backscatter encoding and passive beamforming.
	For single-user scenario, when primary link is absolutely prioritized, the distribution falls on one state and Metascatter boils down to conventional \gls{ris}.
	When only considering backscatter performance, the distribution involves the highest entropy and Metascatter is essentially an \gls{ambc} node.
